Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2018-10-07 paper.tex
ref response 4: clarify NuLib and LS180 reference

The opacity table is computed using \lstinline{NuLib}
\cite{ocon2015-gr1d_with_nu}
and is identical to the LS180 opacity table used in the referenced paper.
The scattering opacity is computed taking into account elastic scattering on
nucleons, alpha particles, and heavy nuclei.
The absorption opacities consist of electron neutrino absorption on neutrons
and heavy nuclei as well as electron antineutrino absorption on protons.
We use Kirchhoff's law to compute emissivities based on these absorption
opacities.
For heavy lepton neutrinos we consider thermal emission processes including
electron-positron annihilation and nucleon-nucleon Bremsstrahlung.
The table is stored on a grid covering energy, density, temperature,
and composition
ranges spanning $\varepsilon_i\in[1,280.5]$~MeV logarithmically,
$\varrho\in[10^6,6.3\times10^{15}]\,{\rm g}\,{\rm cm}^{-3}$ logarithmically,
$T\in[0.05,200]$~MeV logarithmically, and 
$Y_e\in[0.035,0.55]$ linearly,
with grid extents$\{18,82,65,51\}$ respectively.
Interpolation is performed linearly.

>>>>

The opacity table is computed using \lstinline{NuLib},
an open-source neutrino interaction library,
and is identical to the LS180 opacity table used in the paper introducing
that tool \cite{ocon2015-gr1d_with_nu}.
The scattering opacity is computed taking into account elastic scattering on
nucleons, alpha particles, and heavy nuclei.
The absorption opacities consist of electron neutrino absorption on neutrons
and heavy nuclei as well as electron antineutrino absorption on protons.
We use Kirchhoff's law to compute emissivities based on these absorption
opacities.
For heavy lepton neutrinos we consider thermal emission processes including
electron-positron annihilation and nucleon-nucleon Bremsstrahlung.
The table is stored on a grid covering energy, density, temperature,
and composition
ranges spanning $\varepsilon_i\in[1,280.5]$~MeV logarithmically,
$\varrho\in[10^6,6.3\times10^{15}]\,{\rm g}\,{\rm cm}^{-3}$ logarithmically,
$T\in[0.05,200]$~MeV logarithmically, and 
$Y_e\in[0.035,0.55]$ linearly,
with grid extents$\{18,82,65,51\}$ respectively.
Interpolation is performed linearly.
